First we look at the data if there's missing values.
```{r}
skim(election2020_results)
#We can see that there are 9 missing values. 
```
We need to clean up the missing values. 
```{r}
#remove missing values
election2020_results <- na.omit(election2020_results)

```

Then, calculate the rate of votes for Trump in each county. 

```{r, vote rate}
vote_data <- election2020_results %>% 
  select(county_name, fips, candidate, candidatevotes, totalvotes) %>% 
  filter(candidate == "DONALD J TRUMP") %>% 
  group_by(county_name, fips, totalvotes) %>% 
  summarise(vote_sum = sum(candidatevotes)) %>% 
  mutate(vote_rate = vote_sum/totalvotes)
```

Then, filter the most recent data from vaccinations, in this case, september data.

```{r}
sept_vaccinations <- vaccinations %>% 
  select(date, fips,series_complete_pop_pct) %>% 
  filter(date == "09/04/2021")

#After we filtered the dataset, we can conduct cleaning so that the code is more efficient regarding to a smaller dataset.
sept_vaccinations <- na.omit(sept_vaccinations) %>% 
  unique()
```

Next, join the september vaccination percentage to the percentage of votes for each county by each candidate.


```{r}

pct_trump_votes_vacc <- inner_join (vote_data, 
                               sept_vaccinations , 
                               by="fips")

```

Next, join the population size for each county into the percentage trump votes vaccination table.

```{r}

votes_vacc_pop <- inner_join (pct_trump_votes_vacc, 
                               population , 
                               by="fips")
####to filter out the 0-values

```

Then, plot the relationship between percentage of trump vote and percentage of population vaccinated.

```{r}
vac_pop_plot <- votes_vacc_pop %>% 
  ggplot(aes(x=vote_rate,y=series_complete_pop_pct/100, size=pop_estimate_2019)) + 
  
  #fit a regression line to the plot
  geom_smooth(method=lm) + 
  
  #aethetics for population size
  geom_point(color = "black", alpha = .6) +
  scale_size(range = c(0, 30)) +
  
  #draw the dash lines
  geom_hline(yintercept=0.85, linetype="dashed") +
  geom_hline(yintercept=0.539, linetype="dashed") +
  geom_hline(yintercept=0.508, linetype="dashed") +
  
  #break the graph into 3x3 grids with solid lines
  geom_hline(yintercept=0.4, linetype="solid") +
  geom_hline(yintercept=0.6, linetype="solid") +
  geom_vline(xintercept=0.4, linetype="solid") +
  geom_vline(xintercept=0.6, linetype="solid") +
  labs(title = "COVID 19 VACCINATION LEVELS OUT OF TOTAL POPULATION BY COUNTY", 
       x = "2020 Trump Vote %", 
       y = "% of Total Population Vaccinated") +
  NULL

#add the text messages
vac_pop_plot + annotate("text", x = 0.1,y = 0.89, label = "Herd Immunity Threshold (?)",color = 'blue',size = 3) +
  annotate("text", x = 0.05, y = 0.56, label = "TARGET:53.9%", fontface = 'italic', color = 'blue',size = 3) +
  annotate("text", x = 0.05, y = 0.525, label = "ACTUAL:50.8%", fontface = 'italic', color = 'blue',size = 3)+
  annotate("text", x = 0.2, y = 0.1, label = "09/04/2021", fontface = 'italic', color = 'red') +
  annotate("text", x = 0.45, y = 1, label = "EVERY U.S. COUNTY", size = 6) +
  scale_y_continuous(labels = scales::percent)+
  scale_x_continuous(labels = scales::percent, limits = c(0,1))

```